Designing an Agent for an Active Guidance System for Object Search

### 2018-11-21 paper.tex
Added author references

Researchers have begun implementing active search and perception~\cite{aloimonos2013active} strategies in robots (CITE) and image classifiers (CITE) in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.

In (CITE CLASSIFIER), the authors implemented an active search strategy for classifying objects within cluttered images. Their approaches use different methods, but both involve using a model to generate windows of interest to submit to a classifier for classification. The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets, and are iteratively changed based on the output from the respective models. The advantage of their approaches over their contemporaries is that far fewer windows are generated and submitted to the classifier, resulting in lower object classification times. They also report comparable accuracy when compared to their contemporaries.

Similarly, roboticists have moved to incorporate similar strategies on robotic platforms to improve autonomous object search, manipulation and localisation tasks. The authors in (CITE A* PAPER) developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment. In (CITE MDP ROBOT), the authors implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations. However, the authors trained their MDP using a custom object-placement and configuration probabilities and have shown that the results are sensitive to changes within this distribution.

>>>>

Researchers have begun implementing active search and perception~\cite{aloimonos2013active} strategies in robots and image classifiers in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.

In~\cite{caicedo2015active,gonzalez2015active}, the authors implemented an active search strategy for classifying objects within cluttered images. Their approaches use different methods, but both involve using a model to generate windows of interest to submit to a classifier for classification. The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets, and are iteratively changed based on the output from the respective models. The advantage of their approaches over their contemporaries is that far fewer windows are generated and submitted to the classifier, resulting in lower object classification times. They also report comparable accuracy when compared to their contemporaries.

Similarly, roboticists have moved to incorporate similar strategies on robotic platforms to improve autonomous object search, manipulation and localisation tasks. The authors in~\cite{dogar2014object} developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment. In~\cite{aydemir2011search}, the authors implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations. However, the authors trained their MDP using a custom object-placement and configuration probabilities and have shown that the results are sensitive to changes within this distribution.
